Low-lying collective excited states in non-integrable pairing models based on stationary phase approximation to the path integral

### 2018-10-25 paper2/draft1-3.tex
small change

It should be noted that the second excited state in the collective path
corresponds to the $0_4^+$ state,
not to the $0_3^+$ state, in the exact calculation. 
We examine the interband $(k\neq k')$ pair addition transition,
\begin{equation}
B(P_{\rm ad};k\rightarrow k') \equiv 
	\left|\bra{0_{k'}^+;N+2} S^+ \ket{0_k^+;N}\right|^2 ,
\label{BPad}
\end{equation}
in the exact solution.
$B(P_{\rm ad};0_2^+\rightarrow 0_3^+)$ 
is $10\sim100$ times smaller than $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$,
while $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and
$B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$ are in the same order.
The ASCC+SPA produces states in the same family,
namely, those belonging to the same collective subspace (path).
In the phonon-like picture,
we expect similar magnitude of strengths for
$B(P_{\rm ad};{\rm g.s.}\rightarrow i{\rm 1 phonon})$
and
$B(P_{\rm ad};{\rm 1 phonon}\rightarrow i{\rm 2 phonon})$,
but smaller values of
$B(P_{\rm ad};{\rm g.s.}\rightarrow i{\rm 2 phonon})$.
Thus, the $0_4^+$ state in the exact calculation
corresponds to the two-phonon state in the ASCC+SPA.
The $0_3^+$ state in the exact calculation may correspond to
a collective path associated with another solution of the moving-frame QRPA
(thin black line in Fig.~\ref{omega_sq}).

@@

Next, we calculate the wave functions,
according to Eqs.~(\ref{SPA2}) and (\ref{SPA3}).
The ground state corresponds to the number-projected HFB state
(variation before projection).
In contrast, excited states are given as superposition of
generalized Slater determinants in the collective subspace,
Using these wave function of excited states, 
the pair addition transition strengths
are shown in Fig. \ref{3levelPad}.
For the intraband transition ($k=k'$ in Eq. (\ref{BPad}),
the ASCC+SPA method well reproduces the strengths of the exact calculation.
The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
are perfectly reproduced, while
$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are underestimated 
by about $10\%\sim20\%$.

>>>>

It should be noted that the second excited state in the collective path
corresponds to the $0_4^+$ state,
not to the $0_3^+$ state, in the exact calculation. 
We examine the interband $(k\neq k')$ pair addition transition,
\begin{equation}
B(P_{\rm ad};k\rightarrow k') \equiv 
	\left|\bra{0_{k'}^+;N+2} S^+ \ket{0_k^+;N}\right|^2 ,
\label{BPad}
\end{equation}
in the exact solution.
$B(P_{\rm ad};0_2^+\rightarrow 0_3^+)$ 
is $10\sim100$ times smaller than $B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$,
while $B(P_{\rm ad};0_1^+\rightarrow 0_2^+)$ and
$B(P_{\rm ad};0_1^+\rightarrow 0_3^+)$ are in the same order.
The ASCC+SPA produces states in the same family,
namely, those belonging to the same collective subspace (path).
In the phonon-like picture,
we expect similar magnitude of strengths for
$B(P_{\rm ad};{\rm g.s.}\rightarrow {\rm 1-phonon})$
and
$B(P_{\rm ad};{\rm 1-phonon}\rightarrow i{\rm 2-phonon})$,
but smaller values of
$B(P_{\rm ad};{\rm g.s.}\rightarrow {\rm 2-phonon})$.
Thus, the $0_4^+$ state in the exact calculation
corresponds to the two-phonon state in the ASCC+SPA.
The $0_3^+$ state in the exact calculation may correspond to
a collective path associated with another solution of the moving-frame QRPA
(thin black line in Fig.~\ref{omega_sq}).

@@

Next, we calculate the wave functions,
according to Eqs.~(\ref{SPA2}) and (\ref{SPA3}).
The ground state corresponds to the number-projected HFB state
(variation before projection).
In contrast, excited states are given as superposition of
generalized Slater determinants in the collective subspace,
Using these wave function of excited states, 
the pair addition transition strengths
are shown in Fig. \ref{3levelPad}.
For the intraband transition ($k=k'$ in Eq. (\ref{BPad})),
the ASCC+SPA method well reproduces the strengths of the exact calculation.
The ground-to-ground transitions, $B(P_{\rm ad};0_1^+\rightarrow 0_1^+)$
are perfectly reproduced, while
$B(P_{\rm ad};0_2^+\rightarrow 0_2^+)$ are underestimated 
by about $10\%\sim20\%$.
